
\vspace{1.0cm}

\section*{\centering Research Statement \hfill Ghulam Mujtaba \hfill\hspace*{\fill}\monthYear}

\vspace*{5pt}





\section*{OVERVIEW}
\justifying
I am deeply committed to advancing the field of on-device computation, ...

Notably, I introduced innovative techniques for personalized trailer and summarization generation, extracting key events from lightweight video thumbnails instead of processing entire videos. This approach has resulted in a substantial reduction in computational complexity and overhead compared to conventional server-side methods [1, 2, 3]. Additionally, I developed a groundbreaking client-driven GIF generation method that harnesses acoustic features to efficiently identify climactic moments [4]. In a separate but equally impactful endeavor, I devised an energy-efficient smartphone encryption solution, facilitating the seamless integration of security features into video analytics frameworks [2]. These contributions collectively demonstrate the feasibility of conducting sophisticated multimedia tasks in real-time on resource-constrained devices, consistently achieving noticeable computational efficiency gains, often surpassing baseline approaches by a factor of 3 to 4 [5, 6]. Furthermore, qualitative assessments underscore the user-centric nature of my research, as users consistently favor personalized generated content by my techniques [7].


In addition ...


\section*{SPECIFIC RESEARCH INTERESTS}

My research has made significant strides in several domains, including multimedia content analysis, video summarization, ...

% \vspace*{5pt}


\subsection{Project 1}
Add the project description here

\subsection{Project 2}
Add the project description here

\subsection{Project 3}
Add the project description here

\subsection{Project 4}
Add the project description here



\section*{FUTURE WORK}
I am deeply committed to 

\vspace*{5pt}

% Sincerely,\\
% \textbf{Ghulam Mujtaba}
\section*{REFERENCES}
\begin{enumerate}[label={[{\arabic*}]}, align=left, leftmargin=*]
    \item G. Mujtaba, A. Malik, and E.-S. Ryu, “LTC-SUM: Lightweight client-driven personalized video summarization framework using 2D CNN,” IEEE Access, vol. 10, pp. 103 041–103 055, 2022.
    
    \item G. Mujtaba, J. Choi, and E.-S. Ryu, “Client-driven lightweight method to generate artistic media for feature-length sports videos,” in SIGMAP: Processing of the 19th International Conference on Signal Processing and Multimedia Applications. SCITEPRESS, 2022, pp. 102–111.
    
    \item G. Mujtaba, S. Lee, J. Kim, and E.-S. Ryu, “Client-driven animated gif generation framework using an acoustic feature,” Multimedia Tools and Applications, pp. 1–18, 2021.
    
    \item G. Mujtaba and E.-S. Ryu, “Client-driven personalized trailer framework using thumbnail containers,” IEEE Access, vol. 8, pp. 60 417–60 427, 2020.
    
    \item G. Mujtaba and E-S. Ryu, “Human character-oriented animated gif generation framework,” in MAJICC: Mohammad Ali Jinnah University International Conference on Computing. IEEE, 2021, pp. 1–6.
    
    \item G. Mujtaba and E.-S. Ryu, “Personalized movie trailer using thumbnail containers,” in Proc. Int. Workshop on AI for Smart TV Content Production, Access and Delivery (AI4TV 2019) at ACM Multimedia, 2019.
    
    \item G. Mujtaba, M. Tahir, and M. H. Soomro, “Energy efficient data encryption techniques in smartphones,” Wireless Personal Communications, vol. 106, no. 4, pp. 2023–2035, 2019.
\end{enumerate}
